Title

### 2024-06-09 paper/main.tex

\emph{Causal discovery} is the process of identifying and understanding causal
relationships among variables in a dataset.  To perform any causal effect
estimation using Directed Acyclic Graphs (DAGs) or Structural Equation Models
(SEMs), researchers need to first construct a causal structure. In the field of
DAGs, a lot of attention has been put on developing automated algorithms that
can construct these DAGs from data. These algorithm takes different approaches
to causal discovery such as constraint-based algorithms such as PC and Fast
Causal Infenrece (FCI) where the algorithm tries to match the conditional
independences in the data to the ones impled by the model, score-based methods
such as Hill-Climb Search, Greedy Equivalence Search (GES)  where the algorithm
tries to find a model that has the best score given some scoring metric, and
continuous optimization where the problem is formulated as a constrained
optimization problem such as No Tears, and some hybrid approaches.

@@

We present a similar procedure for modifying DAGs based on expert knowledge and
measure of association. We first use the measure of association to test whether
the association observed in the data is explained by the model structure. Based 
on this testing, we suggest adding edges by ranking them by the most unexplained
association between variables. The researcher can then use expert knowledge to 
decide the direction of the edge between the variables.

>>>>

To perform any causal effect identification or estimation using Directed
Acyclic Graphs (DAGs) or Structural Equation Models (SEMs), researchers need to
first construct a causal structure commonly known as DAG or path diagram. This
process of constructing the casual structure from data is known as \emph{Causal
Discovery}. In the field of DAGs, plenty of algorithms have been developed to
automatically construct DAGs from data. These algorithm takes different
approaches to causal discovery such as Constraint-based algorithms such as PC
and Fast Causal Infenrece (FCI) where the algorithm tries to match the
conditional independences in the data to the ones impled by the model,
score-based methods such as Hill-Climb Search, Greedy Equivalence Search (GES)
where the algorithm tries to find a model that has the best score given some
scoring metric, and continuous optimization where the problem is formulated as
a constrained optimization problem such as No Tears.

@@

In the field of Structural Equation Models (SEMs), models are also typically
constructed by hand. Researchers typically come up with an initial model, which
then they use the data and expert knowledge to make modifications to. This
process is known as \emph{Specification Search}. One of the common ways to do
this is through \emph{modification indices} where a global fit of the model is
measured with different modification to the model.  Utilizing expert knowledge
to select the appropriate modification that gives the maximum improvement to
the global fit.

\todo[inline]{Other methods: Modification indices and Lagrange Multiplier tests to
selectively add edges And using Wald test or z statistics (also known as
critical ratios) for removing edges.}

One of the drawbacks of these global fit metrics is that they do not only test
for the structure but also the fitted parameterization.

We present a similar procedure for modifying DAGs based on expert knowledge and
measure of association. We first use the measure of association to test whether
the association observed in the data is explained by the model structure. 
We can not directly use the local CI tests to make modifications because that would give
way too many independencies and we have no way to rank them.
Based 
on this testing, we suggest adding edges by ranking them by the most unexplained
association between variables. The researcher can then use expert knowledge to 
decide the direction of the edge between the variables.
